Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-01 robdml.tex
tex

\begin{figure}[t]
	\vspace{-1em}
	\includegraphics[width=\columnwidth]{figgaeff.pdf}
	\vspace{-1.5em}
	\caption{GA eff}
\end{figure}

\begin{figure}[t]
	\vspace{-1em}
	\includegraphics[width=\columnwidth]{figics.pdf}
	\vspace{-1.5em}
	\caption{ICS eff}
\end{figure}

\noindent\textbf{II. Gradual Adversary.}

\cref{tab:gaeff}

>>>>

\begin{figure}[t]
	\vspace{-1em}
	\includegraphics[width=\columnwidth]{figgaeff.pdf}
	\vspace{-1.9em}
	\caption{Performance of ``HM[$\mathcal{S},g_\mathsf{LGA}$]'' in
	\cref{tab:gaeff}.}
	\label{fig:gaeff}
\end{figure}

\noindent\textbf{II. Gradual Adversary.}
%
As discussed in \cref{sec:32}, the HM[$\mathcal{S},\mathcal{M}$] may still suffer
from the imbalance between learning the embeddings and gaining adversarial
robustness.
%
Hence, we conduct further experiments %with an improved $H_\mathsf{D}$
following the discussion, as shown in \cref{tab:gaeff} and \cref{fig:gaeff}.
%
Compared to HM[$\mathcal{S},\mathcal{M}$], slightly boosting the hardness in
the late phase of training with $g_\mathsf{B}(\cdot)$ where $\xi{=}0.1$
benefits the ERS, but results in a notably lower R@1;
%
A constant $H_\mathsf{D}$ at the upper bound of Semihard (\ie, $0$; too high
for both early and late phase) renders model collapse;
%
$H_\mathsf{D}$ at the lower bound (\ie, $-\gamma$; too low for the late phase)
leads to insignificant ERS improvement;
%
$H_\mathsf{D}{=}-\gamma/2$ provides a balance between the lower and upper
bound, but still suffers from inflexibility.
%
In contrast, being not susceptible to the problems of other choices,
HM[$\mathcal{S},g_\mathsf{LGA}$] achieves an ERS on par with
HM[$\mathcal{S},\mathcal{M}$], but at the lowest R@1 penalty among all choices.

\begin{figure}[t]
	\vspace{-1em}
	\includegraphics[width=\columnwidth]{figics.pdf}
	\vspace{-1.9em}
	\caption{Performance of ``HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS'' in \cref{tab:ics}.}
\end{figure}
